CorReg: model-based pretreatment for regression with correlated variables. Application in steel industry

### 2014-04-01 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@482 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

This generative model is conditional to $S$, the discrete structure model that is identifiable because we can't permute some regressions in (\ref{SR}) and obtain the same joint distribution $P(X,Y)$, the residuals ($\varepsilon_j$) would not stay Gaussian (see the appendices). These residuals are in the following supposed independent but one can suppose dependencies between them and then use appropriate tools to estimate them and the $\delta_j$ like SUR with Feasible Generalized Least Squares (FGLS) by Zellner \cite{SURzellner} or SPRING \cite{chiquetconf} as mentioned in the introduction.
\\

\subsection{Marginal regression model with decorrelated covariates}
Let $Y \in \mathcal{R}^n$ be a response variable we want to explain with $X$.
We note that (\ref{MainR}) and (\ref{SR}) also give by simple integration on $X_2$ a regression model on $Y$ {\it depending only on uncorrelated covariates $X_1$}:
		\begin{equation}
			Y_{|S,X}=X\beta+\varepsilon_Y =X_1\beta_1+X_2\beta_2+\varepsilon_Y \textrm{ whith } \varepsilon_Y \sim \mathcal{N}(0,\sigma^2_YI_n);	\label{MainR}
		\end{equation}
		where $\beta=(\beta_1,\beta_2) \in  \mathcal{R}^p$ is the vector of the regression coefficients and $I_n$ the identity matrix. 
Knowing (\ref{SR}) we then obtain a marginal regression model:
\begin{eqnarray}
	Y_{|X_1}&=&X_1 (\beta_{1}+ \sum_{j \in I_2}B^{j}_{1}\beta_{j})+  \sum_{j \in I_2}\varepsilon_{j}\beta_{j}+\varepsilon_Y \label{Trueexpl} \\
		&=&X_1 \alpha_1 + X_2\alpha_2 + \varepsilon_{\alpha} \textrm{ where} \alpha_2  = 0.
\end{eqnarray}
We note that it simply is a linear regression on some of the original covariates so we only made a pretreatment on the dataset by setting some coefficients to $0$ because of correlations. These $0$ won't be interpreted as independence with the response variable but as redundant information due to correlations between the covariates. It isa variable pre-selection independent of the response $Y$. As a pretreatment, it allows usage of any method in a seconde time to estimate $\alpha$.
\subsection{Estimator and properties}
	The marginal regression model simply is
	\begin{equation}
		Y_{|X_1}= X_1\alpha_1+ \varepsilon_{\alpha}
	\end{equation}			
		So we have the unbiased estimator of $\alpha$: 
		\begin{equation}
			\hat{\alpha}_{1} = (X'_{1} X_{1})^{-1}X'_{1}Y  \textrm{ and }\hat{\alpha}_{2} = 0
		\end{equation}
		We see in (\ref{Trueexpl}) that it gives an unbiased estimation of $Y$ and $\alpha$
		but in terms of $\beta$ this estimator is biased:
		\begin{equation}
			\operatorname{E}[\hat{\alpha_1}|X_1]=\beta_1+\sum_{j \in I_2}B^{j}_{1}\beta_{j}\textrm{ and }\operatorname{E}[\hat{\alpha_2}|X_1]=0
		\end{equation}
		with variance:
		\begin{equation}
			\operatorname{Var}[\hat{\alpha}_{1}|X_1]= (\sigma^2_Y+\sum_{j \in I_2}\sigma^2_{j}\beta_{j}^2 )(X'_{1} X_{1})^{-1}  \textrm{ and }\operatorname{Var}[\hat{\alpha}_{2}|X_1]= 0 
		\end{equation}
		We see that the variance is reduced compared to OLS described in equation (\ref{eqOLS})(no correlations and smaller matrix give better conditioning ) for small values of $\sigma_j$ $i.e.$ strong correlations.					
			%There is no theoretical guarantee that our model is better. It's just a compromise between numerical issues caused by correlations for estimation and selection versus increased variability due to structural hypothesis. Therefore we made some simulations to compare both methods (see the end of this paper).
			Moreover, the explicit structure is parsimonious and simply consists in linear regressions and thus is easily understood by non statistician, allowing them to have a better knowledge of the phenomenon inside the dataset. Expert knowledge can even be added to the structure.
			 This new model is reduced even without variable selection and is just a linear regression so every method for variable selection in linear regression can be used then,like LASSO or even stepwise \cite{seber2012linear}. Hence we hope to obtain a parsimonious model with { \it two kinds of zeros}: those from decorrelating step and those from selection step, with different meanings.
			 \\
			  A last Ordinary Least Square step is added to improve estimation because penalisation is made to select variables but also shrinks remaining coefficients. This last step allows to keep the benefits of shrinkage (variable selection) without any impact on remaining coefficients (see \cite{SAM10088}).

@@

\section{Numerical results on simulated datasets} \label{sectionsimul}
	\subsection{The datasets}	
	Now we have defined the model and the way to obtain it, we can have a look on some numerical results to see if \textsc{CorReg} 	keeps its promises.
	The \textsc{CorReg} package has been tested on simulated datasets. 
Section \ref{compZ} shows the results obtained in terms of $\hat{S}$. Sections \ref{tableMSEsimtout} and \ref{tableMSEsimgauche} show the results obtained using only \textsc{CorReg}, or \textsc{CorReg} combined with other methods. Tables give both mean and standard deviation of the observed Mean Squared Errors (MSE) on a validation sample of $1 000$ individuals. For each simulation,  $p=40$, $\sigma_Y=10$, $\sigma=0.001$, variables $X_1$ follow Gaussian mixture models of $\lambda=5$ classes which means follow Poisson's law of parameter $\lambda$ and which standard deviation also is $\lambda$. The $B_1^j$ and $\beta_j$ are generated according to the same Poisson law but with a random sign. $S$ only contains binary relationships but \textsc{CorReg} was only constrained to $\max (\hat{p}_1^j)=5$.  
	We used \textsc{Rmixmod} to estimate the densities of each covariate. For each configuration, the walk was launched on $20$ initial structures with a maximum of 9 000 steps each time.

>>>>

This generative model is conditional to $S$, the discrete structure model that is identifiable because we can't permute some regressions in (\ref{SR}) and obtain the same joint distribution $P(X,Y)$, the residuals ($\varepsilon_j$) would not stay Gaussian (see the appendices). These residuals are in the following supposed independent but one can suppose dependencies between them and then use appropriate tools to estimate the $\delta_j$ and $\sigma_j$ like SUR with Feasible Generalized Least Squares (FGLS) by Zellner \cite{SURzellner} or SPRING \cite{chiquetconf} as mentioned in the introduction.
\\

\subsection{Marginal regression model with decorrelated covariates}
Let $Y \in \mathcal{R}^n$ be a response variable we want to explain with $X$:
	\begin{equation}
			Y_{|S,X}=X\beta+\varepsilon_Y =X_1\beta_1+X_2\beta_2+\varepsilon_Y \textrm{ whith } \varepsilon_Y \sim \mathcal{N}(0,\sigma^2_YI_n);	\label{MainR}
		\end{equation}
		where $\beta=(\beta_1,\beta_2) \in  \mathcal{R}^p$ is the vector of the regression coefficients and $I_n$ the identity matrix. 
We note that (\ref{MainR}) and (\ref{SR}) also give by simple integration on $X_2$ a regression model on $Y$ {\it depending only on uncorrelated covariates $X_1$}:
		\begin{equation}
			Y_{|S,X}=X\beta+\varepsilon_Y =X_1\beta_1+X_2\beta_2+\varepsilon_Y
		\end{equation}

Knowing (\ref{SR}) we then obtain a marginal regression model:
\begin{eqnarray}
	Y_{|X_1}&=&X_1 (\beta_{1}+ \sum_{j \in I_2}B^{j}_{1}\beta_{j})+  \sum_{j \in I_2}\varepsilon_{j}\beta_{j}+\varepsilon_Y \label{Trueexpl} \\
		&=&X_1 \alpha_1 + X_2\alpha_2 + \varepsilon_{\alpha} \textrm{ where } \alpha_2  = 0.
\end{eqnarray}
We note that it simply is a linear regression on some of the original covariates so we only made a pretreatment on the dataset by setting some coefficients to $0$ because of correlations. These $0$ won't be interpreted as independence with the response variable but as redundant information due to correlations between the covariates. It isa variable pre-selection independent of the response $Y$. As a pretreatment, it allows usage of any method in a seconde time to estimate $\alpha$.
\subsection{Estimator and properties}
	The marginal regression model simply is
	\begin{equation}
		Y_{|X_1}= X_1\alpha_1+ \varepsilon_{\alpha}
	\end{equation}			
		So we have the unbiased estimator of $\alpha$: 
		\begin{equation}
			\hat{\alpha}_{1} = (X'_{1} X_{1})^{-1}X'_{1}Y  \textrm{ and }\hat{\alpha}_{2} = 0
		\end{equation}
		We see in (\ref{Trueexpl}) that it gives an unbiased estimation of $Y$ and $\alpha$
		but in terms of $\beta$ this estimator is biased:
		\begin{equation}
			\operatorname{E}[\hat{\alpha_1}|X_1]=\beta_1+\sum_{j \in I_2}B^{j}_{1}\beta_{j}\textrm{ and }\operatorname{E}[\hat{\alpha_2}|X_1]=0
		\end{equation}
		with variance:
		\begin{equation}
			\operatorname{Var}[\hat{\alpha}_{1}|X_1]= (\sigma^2_Y+\sum_{j \in I_2}\sigma^2_{j}\beta_{j}^2 )(X'_{1} X_{1})^{-1}  \textrm{ and }\operatorname{Var}[\hat{\alpha}_{2}|X_1]= 0 
		\end{equation}
		We see that the variance is reduced compared to OLS described in equation (\ref{eqOLS})(no correlations and smaller matrix give better conditioning ) for small values of $\sigma_j$ $i.e.$ strong correlations.					
			%There is no theoretical guarantee that our model is better. It's just a compromise between numerical issues caused by correlations for estimation and selection versus increased variability due to structural hypothesis. Therefore we made some simulations to compare both methods (see the end of this paper).
			Moreover, the explicit structure is parsimonious and simply consists in linear regressions and thus is easily understood by non statistician, allowing them to have a better knowledge of the phenomenon inside the dataset. Expert knowledge can even be added to the structure.
			 This new model is reduced even without variable selection and is just a linear regression so every method for variable selection in linear regression can be used then,like LASSO or even stepwise \cite{seber2012linear}. Hence we hope to obtain a parsimonious model with { \it two kinds of zeros}: those from decorrelating step and those from selection step, with different meanings.
			 \\
			  A last Ordinary Least Square step is added to improve estimation because penalisation is made to select variables but also shrinks remaining coefficients. This last step allows to keep the benefits of shrinkage (variable selection) without any impact on remaining coefficients (see \cite{SAM10088}).

@@

\section{Numerical results on simulated datasets} \label{sectionsimul}
	\subsection{The datasets}	
	Now we have defined the model and the way to obtain it, we can have a look on some numerical results to see if \textsc{CorReg} 	keeps its promises.
	The \textsc{CorReg} package has been tested on simulated datasets. 
Section \ref{compZ} shows the results obtained in terms of $\hat{S}$. Sections \ref{tableMSEsimtout} and \ref{tableMSEsimgauche} show the results obtained using only \textsc{CorReg}, or \textsc{CorReg} combined with other methods. Tables give both mean and standard deviation of the observed Mean Squared Errors (MSE) on a validation sample of $1 000$ individuals. For each simulation,  $p=40$, $\sigma_Y=10$, $\sigma=0.001$, variables $X_1$ follow Gaussian mixture models of $\lambda=5$ classes which means follow Poisson's law of parameter $\lambda$ and which standard deviation also is $\lambda$. The $\delta_j$ and $\beta_j$ are generated according to the same Poisson law but with a random sign. $S$ only contains binary relationships but \textsc{CorReg} was only constrained to $\max (\hat{p}_1^j)=5$.  
	We used \textsc{Rmixmod} to estimate the densities of each covariate. For each configuration, the walk was launched on $20$ initial structures with a maximum of 9 000 steps each time.
